Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2025-06-19 manuscript/manuscript.tex
small update

To study how the risk of a response, and the accuracy of an emitted response, depends on covariates (i.e., explanatory predictor variables) we can estimate regression models for hazard and for conditional accuracy. Such covariates can be constant over within-trial time (e.g., gender, race, trial number, block number) or vary with within-trial time (e.g., heart rate, eye gaze position, eye pupil dilation). Note that time-varying covariates are not covered in this tutorial.

Heterogeneity

Multilevel survival analysis: Methods, Models and Applications
Austin 2017 !!

fitting problems

@@

In a typical RT data set from a within-subject design, there are N individuals and M repeated measures or trials per experimental condition.
To test process models of cognition, researchers tend to use small-N designs, \ldots{}

Power

>>>>

To study how the risk of a response, and the accuracy of an emitted response, depends on covariates (i.e., explanatory predictor variables) we can estimate regression models for hazard and for conditional accuracy, i.e., perform inferential EHA/SAT analysis. Such covariates can be constant over within-trial time (e.g., gender, race, trial number, block number) or vary with within-trial time (e.g., heart rate, eye gaze position, eye pupil dilation). Note that time-varying covariates are not covered in this tutorial.

Heterogeneity -\textgreater{} Multilevel survival analysis: Methods, Models and Applications
Austin 2017 !!

fitting problems -\textgreater{} Bayesian

@@

In a typical RT data set from a within-subject design, there are N individuals and M repeated measures or trials per experimental condition.
To test process models of cognition, .. advises to use small-N designs, \ldots{} eACH SUBJECT REPLICATION UNIT

Power IS A COMPLEX FUNCTION OF \ldots. (REF A, REF B ON POWER WITH EXPONENTIAL)
